Pillar 1 - Sequential Pattern Mining

### 2019-02-13 Pillar 1 - Sequential Pattern Mining.Rmd
adds a space

```{r SR edit}
    mutate_at(
      c("support",
        "confidence", "lift"),
      funs(round(., 5))
    ) %>%
    filter(!`LHS Course ID`==`RHS Course ID`) %>%
    select(-`LHS Course ID`, -`LHS Quality`, -`RHS Course ID`, -`RHS Quality`)
```

>>>>

```{r SR edit}
    mutate_at(
      c("support",
        "confidence", "lift"),
      funs(round(., 5))
    ) %>%
    filter(!`LHS Course ID` == `RHS Course ID`) %>%
    select(-`LHS Course ID`, -`LHS Quality`, -`RHS Course ID`, -`RHS Quality`)
```
